### 2024-04-08 course/statml/2024/project/project.tex
lecture07

%\section{Kaggle: G-Research Crypto Forecasting}
%
%%\subsection{Project Overview}
%Over USD40 billion worth of cryptocurrencies are traded every day. They are among the most popular assets for speculation and investment, yet have proven wildly volatile. Fast-fluctuating prices have made millionaires of a lucky few, and delivered crushing losses to others. Could some of these price movements have been predicted in advance?
%
%In this competition, you'll use your machine learning expertise to forecast short term returns in 14 popular cryptocurrencies. We have amassed a dataset of millions of rows of high-frequency market data dating back to 2018 which you can use to build your model. Once the submission deadline has passed, your final score will be calculated over the following 3 months using live crypto data as it is collected.
%
%\url{https://www.kaggle.com/c/g-research-crypto-forecasting}
%
%
%%\subsection{Problem Identification}
%%The cryptocurrency market has been skyrocketing recently, and it is estimated that over USD40 billion worth of cryptocurrencies are traded every single day. Cryptocurrencies have become one of the most popular and trending assets for speculation and investment, however, it has been proven to be wildly volatile, where a person can make a fortune and become a millionaire in one day, and lose all his assets the day after. While a few people have made a great fortune through the fast-fluctuating prices, others have been experiencing losses. Hence, we would like to try whether we can predict some of these price movements in advance and forecast short term returns in 14 popular cryptocurrencies through machine learning techniques.
%
%\subsection{Background Knowledge}
%The simultaneous activity of thousands of traders ensures that most signals will be transitory, persistent alpha will be exceptionally difficult to find, and the danger of overfitting will be considerable. In addition, since 2018, interest in the cryptomarket has exploded, so the volatility and correlation structure in our data are likely to be highly non-stationary. The successful contestant will pay careful attention to these considerations, and in the process gain valuable insight into the art and science of financial forecasting.
%
%\subsection{Model and Methods}
%Given a time-series based dataset of cryptocurrency prices, one can use the hierarchical time series model, which is to train a model for all time, models per weekday, model per day, etc. and ensemble them together. Multiple popular models could be applied and you might conduct research about the effectiveness of these models. For example, LSTM is popular among quantitative finance fields, as it can capture the relationship between previous cryptocurrency prices. Since cryptocurrency price is a time-dependent variable, multiple time-series prediction models may also be adopted, like traditional ARIMA, GARCH, and Dynamic linear model. You are welcome to create innovative methods, bringing more insights to the quantitative finance field.  
% 
%\subsection{Data Source}
%Kaggle link: 
%
%\url{https://www.kaggle.com/c/g-research-crypto-forecasting/data}

%They have amassed a dataset of millions of rows of high-frequency market data dating back to 2018 which we can use to build our model. Once the submission deadline has passed, our final score will be calculated over the following 3 months using live crypto data as it is collected.

@@

%You are provided with historical minute-level OHLCV data of 4 major cryto currenciesâ BTC, EOS, ETH, TRX. The raw data is downloaded through a web crawler, which contains information including OHLCV and number of trades. After preprocessing, the minute-bar data in the standard OHLCV format is obtained. 

>>>>

\section{Kaggle: G-Research Crypto Forecasting}

%\subsection{Project Overview}
Over USD40 billion worth of cryptocurrencies are traded every day. They are among the most popular assets for speculation and investment, yet have proven wildly volatile. Fast-fluctuating prices have made millionaires of a lucky few, and delivered crushing losses to others. Could some of these price movements have been predicted in advance?

In this competition, you'll use your machine learning expertise to forecast short term returns in 14 popular cryptocurrencies. We have amassed a dataset of millions of rows of high-frequency market data dating back to 2018 which you can use to build your model. Once the submission deadline has passed, your final score will be calculated over the following 3 months using live crypto data as it is collected.

\url{https://www.kaggle.com/c/g-research-crypto-forecasting}

%\subsection{Problem Identification}
%The cryptocurrency market has been skyrocketing recently, and it is estimated that over USD40 billion worth of cryptocurrencies are traded every single day. Cryptocurrencies have become one of the most popular and trending assets for speculation and investment, however, it has been proven to be wildly volatile, where a person can make a fortune and become a millionaire in one day, and lose all his assets the day after. While a few people have made a great fortune through the fast-fluctuating prices, others have been experiencing losses. Hence, we would like to try whether we can predict some of these price movements in advance and forecast short term returns in 14 popular cryptocurrencies through machine learning techniques.

\subsection{Background Knowledge}
The simultaneous activity of thousands of traders ensures that most signals will be transitory, persistent alpha will be exceptionally difficult to find, and the danger of overfitting will be considerable. In addition, since 2018, interest in the cryptomarket has exploded, so the volatility and correlation structure in our data are likely to be highly non-stationary. The successful contestant will pay careful attention to these considerations, and in the process gain valuable insight into the art and science of financial forecasting.

\subsection{Model and Methods}
Given a time-series based dataset of cryptocurrency prices, one can use the hierarchical time series model, which is to train a model for all time, models per weekday, model per day, etc. and ensemble them together. Multiple popular models could be applied and you might conduct research about the effectiveness of these models. For example, LSTM is popular among quantitative finance fields, as it can capture the relationship between previous cryptocurrency prices. Since cryptocurrency price is a time-dependent variable, multiple time-series prediction models may also be adopted, like traditional ARIMA, GARCH, and Dynamic linear model. You are welcome to create innovative methods, bringing more insights to the quantitative finance field.

\subsection{Data Source}
Kaggle link:

\url{https://www.kaggle.com/c/g-research-crypto-forecasting/data}

They have amassed a dataset of millions of rows of high-frequency market data dating back to 2018 which we can use to build our model. Once the submission deadline has passed, our final score will be calculated over the following 3 months using live crypto data as it is collected.

@@

%You are provided with historical minute-level OHLCV data of 4 major cryto currencies BTC, EOS, ETH, TRX. The raw data is downloaded through a web crawler, which contains information including OHLCV and number of trades. After preprocessing, the minute-bar data in the standard OHLCV format is obtained. 
